A New Metric for the Analysis of Swarms

### 2018-06-07 paper.tex
Stuff
Updates

\markboth
{Eliot \headeretal: An Improved Metric for the Analysis of Swarms}
{Eliot \headeretal: An Improved Metric for the Analysis of Swarms}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=13cm]{figures/FIELDFILL-MAG}
{Cohesion/Repulsion metric 0-120 seconds.\label{emerge:FIELDFILL-MAG}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=13cm]{figures/FIELDFILL-DIST}
{Distance metric 0-120 seconds.\label{emerge:FIELDFILL-DIST}}

>>>>

\markboth
{Eliot \headeretal: A New Metric for the Analysis of Swarms}
{Eliot \headeretal: A New Metric for the Analysis of Swarms}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=14cm]{figures/FIELDFILL-MAG}
{Cohesion/Repulsion metric 0-120 seconds.\label{emerge:FIELDFILL-MAG}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=14cm]{figures/FIELDFILL-DIST}
{Distance metric 0-120 seconds.\label{emerge:FIELDFILL-DIST}}
